\documentclass{article}
\loadcssfile{./style.css}

\begin{document}

\section{Lab 1}
Console generates RF that generate the MR signal.
Magnetic field gradient's control the spatial localization.
Pulse Sequence is a program that controls the gradients and coils to activate them at certain times.

Pulse sequence  is set of controls for  generating pulses and the digitizer. 
Free induction decay (FID) is the signal returned when no spatial localization occurs.
	
A RF pulse tip spins to generate a signal. The Slice Select, Readout (aka Frequency Encode) and the Phase Encode gradients are used to for spatial localization. Repetition Time is TR and Echo Time is TE.

MRI's require homogeneous fields. This means that the strength of the field is relatively even throughout the area being investigated. 
Homogeneity is often measure in terms of parts per million or ppm. 
If the Larmour Frequency were 10 MHz then 1 ppm would be 10 Hz.
Shimming is the process of improving the homogeneity by using shim coils to change the magnetic field distribution.

The MRI takes data in as a set of Kspace data. A Fourier Transform of the k-space data can be taken to reconstruct the image.

PreLab 1
TODO: Bandwidth of RF pulse
TODO: Spectral Width 
TODO: Full-width Half maximum
TODO: FOV Matrix size to resolution
TODO: Imaging planes (Axial Sagital ...)

\section{Lab 2}
The Slice Selection Pulse tips the spins in the region we are interested in investigating.
The 180 or refocusing pulse is used in spin echos to flip the tips 180 degrees. 
The signal is acquired as the frequency encoding gradient is producing spatial localization in that direction.


\subsection{Larmour Frequency Equation}

$ \omega = \gamma * B_0$

$\gamma = 2*pi*42.57*10^6 [rad*Hz/T] $

$ T = 10^4 G$

The Larmour Frequency is the resonant frequency of spins present in a magnetic field of a certain strength.

\subsection{Frequency Encode Gradient Equation}
$ BW_{fe} [rad/sec] = \gamma * G_{fe}*FOV_{fe}$

Note: This is the frequency encode band width not pulse!

$ Sampling Rate = $


\subsection{Slice Selection }
$ Slice Thickness = \Delta z$

$ \Delta z = \frac{BW_{pulse} [rad/sec]}{\gamma G_{ss}}$

$ 1 [G/cm] = 425.7 [Hz/mm]$

Because a narrower bandwidth means a longer RF pulse which would change timings, the slice thickness is typically changed by the gradient strength. To generate a relatively uniform tip over all bandwidths, we use a sinc pulse as its Fourier Transform is a rectangular pulse.

\subsection{Sinc Pulse Notes}
Period of a sinc pulse is the time from its peak to first null. 
The bandwidth in Hz is the inverse of this time.

\subsection{Slice Rephase}
If the tips of the spins are knocked down at the middle of the sinc pulse then the spins at different distances precess at different frequencies. This results in a phase offset based on position. Therefore a spin at distance z  for a sinc pulse of length Tp will have an offset of $\phi(z) = \gamma * G_{ss}*z*\frac{T_p}{2} $. 
If the spins are knocked down at the center point of the sinc then they only dephase for half of the pulse length $\frac{T_P}{2}$. 

To address this dephasing, we apply a gradient withe the opposite sign for $\frac{T_P}{2}$ which will result in a total net phase of 0.
Notes: To account for gradients the general equation is ${\int ^{t=\frac{T_{P}}{2}+ramp}}_{t=0}G_{ss}(t)dt = - \int_{t=rewind\_pulse}G_{rw}(t)dt $

\subsection{Frequency Encoding}
The gradient in this direction maps a frequency value to a position. When we get a signal back from the echo, we can determine its position based on its frequency. 

The frequency encode gradient also causes the phase accumulation which means we must dephase cancel out this effect. We need the frequency dephase pulse to have the same area as the first half of the frequency encoding pulse so that the total net dephase is 0. 
Important Note: The 180 degree pulse flips the sign of our phase. If the frequency encode dephase is after the 180 it will be the opposite sign of the frequency encoding  pulse if its before it will be the same sign. 
This goes for all dephasing pulses.

\subsection{Gradient Waveforms and Eddy Currents}
Producing the desired gradient pulse is not as simple as sending an exact digital copy of the signal we want to the gradient amplifiers. Instead, we have to deal with the realities that the gradients have rise times resulting from being inductors and other non ideal characteristics that we must address. 
To get our desired output, we send a predistorted waveform. The predistortion is called pre-emphasis. It compensates for the transfer function of the entire system.

The ideal waveforms can be seen on the console. The predistorted waveforms can be seen going into the amplifier and out from the amplifier we can see the actual produced currents. The actual magnetic field gradients are not exactly any of these measurements due to eddy currents.

\section{Lab 3}
Discusses T1, T2, TR, and TE parameters.
T1 and T2 are relaxation parameters that effect the contrast between different tissues. 
The Image intensity equation $I(x,y) = M_z^0 (x,y)(1-e^{\frac{-TR}{T_1(x,y)}})*e^{\frac{-TE}{T2(x,y)}}$

A T1 weighting occurs when we reduce the impact of T2 relaxation. A super short TE and TR on the order of T1 would obtain an image whose contrast is mainly determined by the T1. For a T2 weighted image we would have a TE on the order of T2 with a long TR.

By collecting three images, two with the same TR but different TE and two with the same TE but different TR values. We can then use the intensity equation to find the values for T2 and T1 by the two data sets.

You can analytically solve for T2 from the ratio of the Intensity equation of two images to find $T_2  =\frac{TE_2-TE_1}{ln(\frac{I_1}{I_2})}$
T1 requires you to find a best fit curve.

\subsection{T1}
T1 is the relaxation of the tip angle back to 0 degrees from whatever angle it was tipped to.

\subsection{T2}
T2 is the loss of signal due to dephasing of spins in the transverse plane.

\section{Lab 4}
Signal to Noise Ratio = SNR

Issues with averaging just a block of air as noise:
\begin{itemize}
	\item[--] FOV is completely filled
\item[--] Phase encode jitter spreads the noise out
\item[--] Using an array coil
\end{itemize}

We prefer to use standard deviation to measure the noise. 
Ideal snr measurement would take repeated scans over the course of a year.

\subsection{SNR Metrics}

$ SNR_{simple} = \frac{m(signal)}{m(noise)}$

$ SNR_{mean} = \frac{m(signal)}{\sqrt{\frac{2}{\pi}}m(noise)=1.26*SNR_{simple}}$

$ SNR_{std} = \frac{m(signal)}{\sqrt{\frac{2}{4-\pi}}std(noise)}= 0.655\frac{m(signal)}{std(noise)}$

For the SNR difference method, obtain two identical images then take the mean of the sum of the mean of the difference.

$ SNR_{diff} = \frac{\frac{1}{2}m(sum)}{\frac{1}{\sqrt{2}}m(diff)}= \frac{m(sum)}{\sqrt{2}m(diff)}$

For the SNR zero method, obtain two images but one with the tip angle set to 0 so any transmitter noise is still present.

Then you can use either $SNR_{mean}$ or $SNR_{std}$ with the noise coming from the second image.


\subsection{SNR Equation}

$ SNR = K* (Voxel\_Size) * \frac{\sqrt{Measurements}}{\sqrt{Bandwidth}} $

For 2D,

\begin{equation}
 SNR_{2D} = K*\frac{FOV_x}{\sqrt{N_x}}*\frac{FOV_y}{\sqrt{N_y}}*Thick*\sqrt{NSA}*\sqrt{\Delta t}
\end{equation}

Variable Meanings:

$ NSA = $ Number of Signal Averages = Number of Excitations

$ FOV = $ The Field of View in a distance unit

$ N_a = $  Number of acquired points in the a direction 

$ \Delta t = \frac{1}{Bandwidth} = N_{fe}/(time sample all N_{fe} points) $  The $ \Delta t$ is the time it takes to sample one point. 

$ Thick = $ The thickness is the size of the slice thickness.

\section{Lab 5}
Shimming and Linewidths
MRI's require uniformity on the scale of ppm.
Generally to 10's off ppm but spectroscopy and gradient echos might be even lower.

Shims are magnets that are used to adjust the main magnetic field to improve homogeneity.
We often shim by sending a hard pulse over the whole phantom and reading the amplitude of the integral of the signal that returns. We then try and maximize this by searching through all of the different currents.

For our FID images we use a very short RF pulse to be sure that we excite all frequencies related to the image. We move off frequency so the fid is oscillatory. 


\subsection{Adjusting One Shim}
Initially, we imaged with all the shims set to 0.
Then to see the impact that the shim will have on the static magnetic field we image +1000 and then -1000 DAC units.

DAC units: different mri scanners have different shims and gradients. DAC (digital to analog converter) handles the input of current into the coils. The max DAC units drives with the max current. 
We want to find the field offset per dac unit.

\subsection{Field and Phase Maps}
We can take the phase of our image and make a map of total phase difference from a point by unwrapping at phase breaks. With inhomogeneities in the magnetic field, phase offsets will occur between the center field strength and other places of field offset because of their different Larmour frequency.

With unwrapped phase we can map the frequency of points:

\begin{equation}
	\Delta f[Hz] = \frac{\Delta \phi[degrees]}{TE[sec]*360\frac{[degrees]}{[cycle]}}
\end{equation}

This frequency can then be used for the field:

\begin{equation}
	\Delta B_0[ppm] = \frac{\Delta f[Hz]}{f_0[MHz]}
\end{equation}

Notes: Linewidth is realted to this but is an average scalar measurement while a Field Map tells us the relative field strength at each point.
We can subtract the -1000 Dac unit image from the +1000 unit image which cancels out the background phase.

Our shim sensitivity units will  be in $Hz/cm^n/Amp$ where n is the order of the shim.

\section{Lab 6}
Two and Three point Dixon Method.
The dixon method is a way of produce images containing just water or just fat in them. The method uses that there is a 3.5 ppm shift in the frequencies of fat and water to separate the two.

The time difference between which they oscillate at is the chemical shift frequency $ f_{cs} = 3.5 ppm$. The water and fat signals start in phase but will go out of phase when the fat signal has rotated one half cycle $a = t_{null}=\frac{1}{2*f_{cs}}$

If the time between the spin-echo and gradient-echo equals $t_{null}$ then the fat and water signals are out of phase.

\subsection{Two-Point Dixon Method}
Produce a standard pulse echo image where both the water and fat will be in phase. Then move the 180 degree pulse by $t_{null}/2$ to produce the out of phase image.
Moving this 180 pulse by a value C causes the difference of the spin echo to be increased by C while at the same time decreasing the gradient echo by C resulting in $ \Delta T = T_se-T_ge = 2*C$ if before the move it equaled 0.
The resulting equations are as follows.

\begin{equation}
	I_1= I_w+I_f \\
	I_2= I_w-I_f \\
	I_w = 0.5*|{I_1+I_2}| \\
	I_f = 0.5*|{I_1-I_2}|
\end{equation}

\subsection{Three-Point Dixon Method}
The three point dixon method adds a third image in addition to the 0 degrees and 180 degrees to help account for phase offset error. This third image is taken at 360 degrees. The phase due to time shift is the same between both the 0 and 360 degree images so the only difference between their phases must be error. The 360 will have accumlated 2 times the phase error of the 180. One half the result of  the phase of the 360 image subtracted by the 0 degree image results in the phase error of the 180 image. By subtracting this result from the 180 image we can then use our new modified 180 and 0 degree image with the 2 point dixon method.

\subsection{Chemical Shift Notes}
The frequency difference between water and fat can result in a black gap appearing between the water and fat in the frequency encode direction .

\begin{equation}
	Chem Shift Pixel # = \frac{\Delta f }{BW/N_x}
\end{equation}

\section{Lab 7}
\subsection{Time of Flight}

\subsection{Phase Velocity Measurement}
A particle moving in a gradient will accumulate phase. By measuring the 


Im not going to be able to finish the write ups till after my exam. Best of luck!
\end{document}

